\documentclass{../presentation}

\title{How Do Enterprise Resource Planning Systems Affect Firm Risk? \\ Post-Implementation Impact.}

\begin{document}
    \maketitle


    \begin{frame}
        \frametitle{Problem / Question}

        Firm risk, i.e. volatility of firm performance.

        \begin{itemize}
            \item Critical, observable by investors
        \end{itemize}

        ERP market growing and takes a dominant position in IT investment.

        \begin{equation*}
            \text{ERP}\uparrow \Longrightarrow \text{Performance Volatility}\downarrow
        \end{equation*}

        Theoretically verified (by \textbf{TOIP}), practically adopted.

        \textbf{Problem}: What is the impact of ERP system on firm risk?

    \end{frame}

    \begin{frame}
        \frametitle{Knowledge}

        \textbf{ERP system and firm performance}: mixed.

        \textbf{ERP deployment stages}: adoption, implementation and \textit{post-implementation}. And how it affects firm risk.

        \textbf{ERP system and business processes}:

        \begin{enumerate}
            \item automation: automatic information processing $\rightarrow$ quick response
            \item standardization: introducing protocols, reducing managerial discretion
            \item integration: value chain $\rightarrow$ information value chain, increasing agility
        \end{enumerate}

        Theory of organizational information processing (\textbf{TOIP}): the interactions of environmental uncertainty and firms. $\rightarrow H_1$

    \end{frame}

    \begin{frame}
        \frametitle{Knowledge}

        \textbf{Value chain theory}, together with ERP system scope $\rightarrow H_{2a}$

        \begin{enumerate}
            \item Functional modules: common infrastructure $\rightarrow H_{2b}$
            \item Operational modules: production control
        \end{enumerate}

        \textbf{Environmental uncertainty}: dynamism and complexity. $\rightarrow H_3$

    \end{frame}

    \begin{frame}
        \frametitle{Instrument}

        Hypothesis testing \& OLS

        \textbf{Model construction}: ERP presence, environmental uncertainty and their co-effects.

        \textbf{Disassembling of ERP system}: number of ERP modules, further functional \& operational modules.

        \textbf{Metrics}: Earning volatility (firm risk), 0-1 indicator (ERP presence and level), previous margin volatility and concentration ratio (environmental uncertainty).

        \textbf{Data}: Compustat database, Computer Intelligence database, 2127 records in total.

    \end{frame}

\end{document}